Exploring the Impact of Atypical Events on Regret: Analysis Through Hitchhiker, Car Accident, and Robbery Scenarios

### 2024-02-14 outputs/paper/paper.qmd
new version of qmd file

---
title: "Exploring the Impact of Atypical Events on Regret: Analysis Through Hitchhiker, Car Accident, and Robbery Scenarios"
subtitle: "Reproduction of 'The impact of past behaviour normality on regret: replication and extension of three experiments of the exceptionality effect' (Lucas Kutscher & Gilad Feldman, 2018)"
author: Dailin(Ben) li, Qisheng Liang, Xutao Chen
thanks: "Code and data are available at: https://github.com/UofT-DailinLi/Impact-of-Atypical-Events-on-Regret.git. A replication of various aspects in this paper are available at: https://doi.org/10.1080/02699931.2018.1504747"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This study aims to replicate Kutscher and Feldman’s findings, which examine regret based on the norm theory. According to norm theory, an individual’s activity can be categorized as either typical or atypical， with the latter, on the other hand, eliciting a stronger emotional response. We focused on replicating three specific scenarios: hitchhiking, car accidents, and robberies. Examining how people recalled their behaviour in these specific scenarios helped our perception of the emotion of regret. This replication is consistent with the original study."

@@

toc: true
toc_depth: 2
number-sections: true
bibliography: references.bib
---

@@

@@

# References

>>>>

---
title: "Exploring the Impact of Atypical Events on Regret: Analysis Through Hitchhiker, Car Accident, and Robbery Scenarios"
subtitle: "Reproduction of 'The impact of past behaviour normality on regret: replication and extension of three experiments of the exceptionality effect' (Lucas Kutscher & Gilad Feldman, 2018)"
author: Dailin(Ben) li, Qisheng Liang, Xutao Chen
thanks: "Code and data are available at: https://github.com/UofT-DailinLi/Impact-of-Atypical-Events-on-Regret.git. A replication of various aspects in this paper are available at: https://doi.org/10.1080/02699931.2018.1504747"
date: today
abstract: "This study aims to replicate Kutscher and Feldman’s findings, which examine regret based on the norm theory. According to norm theory, an individual’s activity can be categorized as either typical or atypical， with the latter, on the other hand, eliciting a stronger emotional response. We focused on replicating three specific scenarios: hitchhiking, car accidents, and robberies. Examining how people recalled their behaviour in these specific scenarios helped our perception of the emotion of regret. This replication is consistent with the original study."

@@

toc: true
toc_depth: 2
number-sections: true
bibliography: references.bib

---

@@

# Discussion

## Bais
Ethical implications and biases naturally arise when collecting quantitative and qualitative data. The data collected in this article were basically provided by the participants. Although efforts were made to screen the participants fairly and make them fully meet the required conditions, in the context of their simple one-to-one comparison, data bias is more likely to occur. For example, when testing for deviant effects, findings showed stronger regret for action than for inaction when using presentations involving the fate of two people, but this effect was very weak when using designs involving a single individual. This suggests that simple comparison scenarios may overestimate the size of the deviant effect.
In addition, because the data used in the article are not original data, the selection of experimental participants may not be representative of a wider population, or the experimental situation may deviate from real-world situations, then these research results may not be widely generalizable to in a broader context, thus illustrating potential sampling bias issues.

## Future
The results obtained in this article can be useful in several fields in the future: firstly in psychology and behavioral economics, with the results regarding the link between the emotion of regret and decision-making behavior, especially when taking into account the regularity of the behavior and deviancy, research on how individuals process decision outcomes and how these processes influence future decisions can be considered at a psychological level. In addition, the findings provide a better understanding of how consumers make decisions based on past behavior and whether those behaviors are routine or unusual. The second is in terms of public policy and education, these findings can provide a better understanding of how people evaluate their own behavior and how these evaluations affect their emotions and behavioral intentions, which can help develop more targeted and effective interventions, and also More effective teaching strategies and learning tools can be developed. Finally, it can even be applied to artificial intelligence and machine learning, which has also been a hot topic in recent years. When designing intelligent systems, these research results can provide information about the process and results of how humans make decisions, and can help developers create algorithms that are more consistent with human behavior and emotional responses.

@@

\newpage
# References
